Star formation laws in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity

### 2015-06-24 draft3.tex
maryam's comment

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel}}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
\begin{document}
% TITLE
\title[STAR FORMATION LAW IN M31]{Star formation law in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
\author[S. Rahmani, et. al.]{S.~Rahmani, S.~Lianou, P.~Barmby\\
Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada}
\maketitle

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end. %PBNew: OK, no comments on this yet.
 We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law. \cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''. Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 \um, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$. We use maps of $^{12}$CO and 21cm emission to produce the \sigmagas map.% For regions that are not covered in the $^{12}$CO map, we used the dust map (obtained from $SPIRE$ data) as a tracer of total gas.
 The stellar mass surface density  map is calculated using mid-infrared IRAC imaging. Our preliminary results from testing the K-S law in M31 find a power-law index of  $N = 0.62 \pm 0.01$, at the low end of values compared with previous work. We determine additional K-S law fits using each SFR map independently with molecular hydrogen, atomic hydrogen and total gas maps. We then repeat the analysis considering the stellar mass density in order to test whether the regular or extended Schmidt laws are more appropriate for M31.

@@

\begin{equation}
\label{equ:ks_org}
\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15}
\end{equation}
which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy. Moreover, \cite{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5 - 2 kpc) in the spiral galaxy M51. To calculate the SFR they used $24 \mu$m plus H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied. They found a correlation, from the radial variation of both the SFR and the gas surface density, with an index of $1.56 \pm 0.04$. %kennicutt07

@@

%P5(2*): What we did and why Andromeda and
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). Additionally, We applied these two laws on three different regions in M31 to determine if there is any dependence on distance from the centre of the galaxy. Since M31 is the nearest spiral galaxy to the Milky Way, we can have higher resolution images of this spiral galaxy. High resolution images provide data from various regions within the galaxy with different physical situations (e.g. metallicity, surface brightness, gas density). This inside look helps us to test star formation laws in diverse physical conditions. Thus, M31 is a suitable test bed for studying scaling laws. %me

Furthermore, the range of the power index of the K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}. Various groups used different methods and data, and have different value for the power index. In the most recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission). The measured power indices for each map and each region vary between 0.6 to 2.03. The origin of these variation in results is still ongoing
question. It is not obvious what makes these differences in the power law indices calculated by different groups. It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law does not work on M31 at all. We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method in results. %me

%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
\section{Data}
\label{sec:data}
Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones. Therefore, a variety of data from gamma-ray to radio wavelengths are available. Wide ranges of data provide us the ability to measure all the required parameters to test the star formation laws in M31. Table~\ref{table:data} lists all the data we used in this paper. Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids. In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12}, to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data. Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size which match with their new resolution. %I do not like this centence but I am not sure how to fixt it.
%PBnew: what exactly does 'highest resolution available' mean? Same for 'proper pixel size' ? /done!

@@

One of the calibrations, which was used to calculate SFR, uses FUV emission as a tracer of the star forming regions. FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \citep{Martin05}). GALEX telescope data contains information for two bands, FUV:1350--1750 and NUV:1750--2750~\AA, with FWHM of 4~\farcs5, and 6~\arcsec.

%\subsection{Visible light}
\label{sec:vislight}
Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission. \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope. \halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between 2000 August and 2002 September. We created a Mosaic image of the maps using the Montage \citep{Berriman08}. Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha image using the averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}. We also took a masked map from \cite{Azimlu11} and masked all foreground star or partially saturated stars(Figure~\ref{fig:halpha}). Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.

%\subsection{IR and sub mm Data}
In IR and sub mm bands, both {\em Spitzer} \citep{Wener04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed the M31. The Infrared Array Camera (IRAC; \citep{Fazio04}) on {\em Spitzer} is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um). IRAC observations of the M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$. IRAC 3.6 and 4.5\um bands  were used to calculate the stellar mass. %PBnew: did you use 4.5um?
Multiband Imaging Photometer for \Spitzer (MIPS) observed the  M31 at 24, 60, and 160\um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.

Calculation of the SFR using TIR emission needs maps of the m31 in 8, 24, 70, and 160 \um. IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used. PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.

%\subsection{Radio Emission}
Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium. This map covers $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper. In this project we also used 21cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}. They used Synthesis telescope and the 26m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21cm band of the M31.

\section{Measuring Star Formation Laws Components}

%----------------------------------------------------------------------------------------
%STAR FORMATION RATE
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsection{Star Formation Rate}
\label{sec:sfr}
\subsubsection{FUV plus 24\um Star Formation Rate}

In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24\um emission introduced by \cite{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.,][]{Kennicutt89}. The UV emission traces recently formed stars with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is really sensitive to dust extinction. On the other hand 24\um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation time scale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24\um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{obs}+3.89L(24\mu m)]
\end{equation}
where a unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$. L(FUV)$_{obs}$ is the luminosity of the galaxy in the FUV emission. The index of "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \cite{Leroy08}. We assumed for any pixel in FUV$_{obs}$ map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out. We also masked the same region in the galaxy for 24\um map. Using this method, we calculated the total SFR is $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fuv.eps}
        \caption{SFR,FUV+24\um}
        \label{fig:sfr,fuv}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_halpha.eps}
        \caption{SFR,H$_{\alpha}$}
        \label{fig:sfr_halpha}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fir.eps}
        \caption{SFR,TIR}
        \label{fig:sfr,fir}
    \end{subfigure}
    \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
    \label{fig:sfrs}
\end{figure*}

\subsubsection{Total Infrared Star Formation Rate}
\label{sec:sfr_fir}
The total infrared emission of a system, can also be used as a tracer of the SFR. Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelengths, however, there is no one-to-one mapping between IR and UV emission. Therefore, integrating over the full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of IR single-band emission \citep{Calzetti13}. \cite{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:

\begin{equation}
\label{equ:sfr_fir}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
\end{equation}
where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$ respectively. Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using the equation ~\ref{equ:sfr_fir} overestimates the SFR in M31.

TIR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths. For the second approach \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity. \cite{Boquien10} tested and modified this calibration as:
\begin{equation}
 \label{equ: TIR}
L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160)
\end{equation}
where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 \um, 24 \um, 70 \um and 160 \um in units of erg~s$^{-1}$. We used equation~\ref{equ:sfr_fir} to calculate the second map of the SFR of M31 (Figure~\ref{fig:sfr,fir}). Using this method we calculated the total SFR as $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$. Table~\ref{table:sfr} compares the total SFR from literature and current work.

\begin{table*}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24\um&0.31 $\pm$ 0.04\\
Current work&\halpha and 24\um&0.35 \\
Current work&TIR luminosity&0.4 $\pm$ 0.04\\
\cite{Ford13}&FUV and 24\um&0.25\\
\cite{Ford13}&TIR luminosity&0.48-0.52\\
\cite{Azimlu11}& \halpha and 24\um&0.34\\
\cite{Azimlu11}&Extinction corrected \halpha&0.44\\
\cite{Tabatabaei10}&Extinction corrected \halpha&0.27--0.38\\
\cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table*}

@@

%----------------------------------------------------------------------------------------
%SFR LAWS
%----------------------------------------------------------------------------------------
\section{Scaling SFR}
\subsection{Star formation laws}

>>>>

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel}}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

\begin{document}
% TITLE
\title[STAR FORMATION LAWs IN M31]{Star formation laws in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
\author[S. Rahmani, et. al.]{S.~Rahmani, S.~Lianou, P.~Barmby\\
Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada}
\maketitle

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end. %PBNew: OK, no comments on this yet.
 We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law. \cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''. Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 $\mu$m, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$. We use maps of $^{12}$CO and 21cm emission to produce the \sigmagas map.% For regions that are not covered in the $^{12}$CO map, we used the dust map (obtained from $SPIRE$ data) as a tracer of total gas.
 The stellar mass surface density  map is calculated using mid-infrared IRAC imaging. Our preliminary results from testing the K-S law in M31 find a power-law index of  $N = 0.62 \pm 0.01$, at the low end of values compared with previous work. We determine additional K-S law fits using each SFR map independently with molecular hydrogen, atomic hydrogen and total gas maps. We then repeat the analysis considering the stellar mass density in order to test whether the regular or extended Schmidt laws are more appropriate for M31.

@@

\begin{equation}
\label{equ:ks_org}
\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15},
\end{equation}
which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy. Moreover, \cite{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5 - 2 kpc) in the spiral galaxy M51. To calculate the SFR they used $24 \mu$m plus H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied. They found a correlation, from the radial variation of both the SFR and the gas surface density, with an index of $1.56 \pm 0.04$. %kennicutt07

@@

%P5(2*): What we did and why Andromeda and
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). Additionally, We applied these two laws on three different regions in M31 to determine if there is any dependence on distance from the centre of the galaxy. Since M31 is the nearest spiral galaxy to the Milky Way, we can have higher resolution images of this spiral galaxy. High resolution images of this spiral galaxy are avaiable that provide data from various regions within the galaxy with different physical properties (e.g. metallicity, surface brightness, gas density). This inside look helps us to test star formation laws in diverse physical conditions. Thus, M31 is a suitable test bed for studying scaling laws. %me

Furthermore, the range of the power index of the K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}. Various groups used different methods and data, and measured different values for the power index. In the most recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission). The measured power indices for each map and each region vary between 0.6 to 2.03. The origin of these variations in the results is still an open
question. It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working on M31. We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method on the results. %me

%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
\section{Data}
\label{sec:data}
Being the closest neighbouring galaxy to our own Milky Way, M31 has extensively been studied using both ground- and space- based telescopes.
%Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones. 
Therefore, large data sets exist on M31 spanning from gamma-ray to radio wavelengths, allowing us to %a variety of data from gamma-ray to radio wavelengths are available. Wide ranges of data provide us the ability to 
measure all the required parameters to test the star formation laws in this galaxy. Table~\ref{table:data} lists the data we used in this paper. Each data comes with a different Full Width Half Maximum (FWHM), spacial resolution and grids. In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12} to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data. Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size matching with their new resolution. %I do not like this centence but I am not sure how to fixt it.
%PBnew: what exactly does 'highest resolution available' mean? Same for 'proper pixel size' ? /done!

@@

One of the calibrations used to calculate SFR uses FUV emission as a tracer of the star forming regions. FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \cite{Martin05}). GALEX telescope data contains information for two bands, FUV:1350--1750 and NUV:1750--2750~\AA, with FWHM of 4~\farcs5, and 6~\arcsec.

%\subsection{Visible light}
\label{sec:vislight}
Our other method to calculate the SFR involved using a combination of \halpha and 24 M emission. \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope. \halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between August 2000 and September 2002. We created a Mosaic image of the maps using the Montage \citep{Berriman08}. Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha image using the averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}. We also took a masked map from \cite{Azimlu11} and masked all foreground or partially saturated stars (Figure~\ref{fig:halpha}). Details about making the \halpha map can be found in Appendix ~\ref{app:halpha}.

%\subsection{IR and sub mm Data}
Both {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed M31 at IR and sub mm bands. Observations with Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8 \um). IRAC observations of M31 were obtained by \cite{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$. IRAC 3.6 \um bands were used to calculate the stellar mass. Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 60, and 160 \um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.

Calculation of the SFR using TIR emission requires maps of M31 in 8, 24, 70, and 160 \um. IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission; however due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used. PACS 160 \um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 $\mu$m, 350 $\mu$m, and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands coveres $\sim 5\degr.5 \times 2\degr.5$ regions in M31 \citep{Fritz12}.

%\subsection{Radio Emission}
Emission from $^{12}$CO (J:$1\rightarrow0$) line that, was observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium. This mapa a region $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper. In this study we also used 21 cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}. They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21 cm band of M31.

\section{Measuring the component of Star Formation Laws}

%----------------------------------------------------------------------------------------
%STAR FORMATION RATE
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsection{Star Formation Rate}
\label{sec:sfr}
\subsubsection{FUV plus 24 M Star Formation Rate}

In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \cite{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.,][]{Kennicutt89}. The UV emission traces recently formed stars with the age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{obs}+3.89L(24\mu m)],
\end{equation}
where SFR is in M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$. L(FUV)$_{obs}$ is the luminosity of the galaxy in the FUV emission. The subscript "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction. Nevertheless, this emission was corrected for the foreground star's emission using a method introduced by \cite{Leroy08}. We assumed for any pixel in FUV$_{obs}$ map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out. We also masked the same region in the galaxy for the 24 \um map. Using this method, we calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fuv.eps}
        \caption{SFR,FUV+24 M}
        \label{fig:sfr,fuv}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_halpha.eps}
        \caption{SFR,H$_{\alpha}$}
        \label{fig:sfr_halpha}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fir.eps}
        \caption{SFR,TIR}
        \label{fig:sfr,fir}
    \end{subfigure}
    \caption{SFR map from a combination of FUV + 24 M emission (top), \halpha and 24 M emission (middle), and total infrared emission (bottom)}
    \label{fig:sfrs}
\end{figure*}

\subsubsection{\halpha plus 24 \um Star Formation Rate}
\label{sec:sfr_halpha}

\subsubsection{Total Infrared Star Formation Rate}
\label{sec:sfr_fir}
The total infrared emission of a system can also be used as a tracer of the SFR. Dust absorbs radiation from hot and young stars and re-emits it at infrared wavelengths; however, there is no one-to-one mapping between IR and UV emission. Therefore, integrating over the full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of IR single-band emission \citep{Calzetti13}. \cite{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$, and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:

\begin{equation}
\label{equ:sfr_fir}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
\end{equation}
where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$, respectively. Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using equation~\ref{equ:sfr_fir} overestimates the SFR in M31.

TIR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data at different IR wavelengths. As a second approach, \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity. \cite{Boquien10} tested and modified this calibration as:
\begin{equation}
 \label{equ: TIR}
L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160),
\end{equation}
where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 $\mu$m, 24 $\mu$m, 70 $\mu$m,and 160 \um in units of erg~s$^{-1}$. We used equation~\ref{equ:sfr_fir} to calculate the second map of the SFR of M31 (Figure~\ref{fig:sfr,fir}). Using this method, we calculated the total SFR to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$. Table~\ref{table:sfr} compares the total SFR from literature and the present work.

\begin{table*}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24 M&0.31 $\pm$ 0.04\\
Current work&\halpha and 24 M&0.35 \\
Current work&TIR luminosity&0.4 $\pm$ 0.04\\
\cite{Ford13}&FUV and 24 M&0.25\\
\cite{Ford13}&TIR luminosity&0.48-0.52\\
\cite{Azimlu11}& \halpha and 24 M&0.34\\
\cite{Azimlu11}&Extinction corrected \halpha&0.44\\
\cite{Tabatabaei10}&Extinction corrected \halpha&0.27--0.38\\
\cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table*}

@@

%----------------------------------------------------------------------------------------
%Metallicity
%----------------------------------------------------------------------------------------
\subsection{Metallicity}
%----------------------------------------------------------------------------------------
%SFR LAWS
%----------------------------------------------------------------------------------------
\section{Scaling SFR}
\subsection{Star formation laws}
